Cluster Paper

### 2015-03-30 ms.tex
commented membership section

\subsection{Membership}
It is expected that some of the galaxies detected will be spurious sources not associated with the any given cluster. To reject these interlopers we employ two methods. For clusters with 20 or more $Q=0$ redshifts we use the  ``shifting gapped" method of \cite{Fadda1996}. This procedure combines both the positional and velocity information. Galaxies are binned in $0.4h^{-1}$ Mpc or larger enough bins to contain at least 10 galaxies. The galaxies in each bin are sorted by their line-of-sight velocity (LOSV),
\begin{equation}
	v = \frac{c (z-z_{cl})}{(1+z_{cl})}
\end{equation}
where $z$ is the redshift of the individual galaxy and $z_{cl}$ is the average redshift of the cluster. Any galaxy with a LOSV greater than 1000 \kms of a neighboring galaxy is rejected as an interloper. The procedure repeats until the number of galaxies stabilizes in the bin.

For galaxy clusters with fewer than 20 $Q=0$ redshifts we employ the method outlined in \cite{Connelly2012,Wilman2005} where we assume an initial velocity dispersion of 500\kms\ and apply both redshift and spatial limits given by:
\begin{equation}
	\delta(r)_{max} = \frac{1}{10}\frac{\delta(z)_{max}}{h_{75}^{-1}\mathrm{Mpc}}
\end{equation}
and
\begin{equation}
	\delta(\theta)_{max} = 206265'' \frac{\delta(r)_{max}}{h_{75}^{-1}\mathrm{Mpc}} \bigg{(}\frac{D_{\theta}}{h_{75}^{-1}\mathrm{Mpc}} \bigg{)}.
\end{equation}
where $\delta(z)_{max} = 2\sigma(v)/c$ and $D_\theta$ is the angular diameter distance.

>>>>

%\subsection{Membership}
%It is expected that some of the galaxies detected will be spurious sources not associated with the any given cluster. To reject these interlopers we employ two methods. For clusters with 20 or more $Q=0$ redshifts we use the  ``shifting gapped" method of \cite{Fadda1996}. This procedure combines both the positional and velocity information. Galaxies are binned in $0.4h^{-1}$ Mpc or larger enough bins to contain at least 10 galaxies. The galaxies in each bin are sorted by their line-of-sight velocity (LOSV),
%\begin{equation}
%	v = \frac{c (z-z_{cl})}{(1+z_{cl})}
%\end{equation}
%where $z$ is the redshift of the individual galaxy and $z_{cl}$ is the average redshift of the cluster. Any galaxy with a LOSV greater than 1000 \kms of a neighboring galaxy is rejected as an interloper. The procedure repeats until the number of galaxies stabilizes in the bin.

%For galaxy clusters with fewer than 20 $Q=0$ redshifts we employ the method outlined in \cite{Connelly2012,Wilman2005} where we assume an initial velocity dispersion of 500\kms\ and apply both redshift and spatial limits given by:
%\begin{equation}
%	\delta(r)_{max} = \frac{1}{10}\frac{\delta(z)_{max}}{h_{75}^{-1}\mathrm{Mpc}}
%\end{equation}
%and
%\begin{equation}
%	\delta(\theta)_{max} = 206265'' \frac{\delta(r)_{max}}{h_{75}^{-1}\mathrm{Mpc}} \bigg{(}\frac{D_{\theta}}{h_{75}^{-1}\mathrm{Mpc}} \bigg{)}.
%\end{equation}
%where $\delta(z)_{max} = 2\sigma(v)/c$ and $D_\theta$ is the angular diameter distance.
